Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2015-11-10 fib2.tex
show a glueing map

We list the axioms for a \emph{2-dimensional unitary topological modular functor}.
 % abbreviated as \emph{MF}.
For the details of this construction, see
\cite{Turaev1994}, \cite{Walker1991} or \cite{Bakalov2000}.
For a more pedestrian treatment, see \cite{Freedman2002simulation} or \cite{Beverland2004.}

@@

{\bf Axiom III.}
%Gluing.
Denote a surface $M$ with (at least) two boundary
components labelled $a, b$ as $M_{a,b}$. 
Let $N$ be the surface obtained from $M$ by gluing
these two boundary components together.
If we constrain $b=\hat{a}$ then the fusion space
of $M_{a,\hat{a}}$ embedds unitarily in the fusion
space of $N.$ Moreover, there is a unitary map
$$
    \bigoplus_{a\in\mathbb{A}} \F(M_{a,\hat{a}}) \to \F(N).
$$
A common operation is to glue two separate surfaces.
We can do this by first taking disjoint union (tensoring
the fusion spaces)
and then gluing.

>>>>

We list the axioms for a 
\emph{2-dimensional unitary topological modular functor}.
 % abbreviated as \emph{MF}.
There are quite alot of details that we leave out,
%For the details of this construction, see
see
\cite{Turaev1994}, \cite{Walker1991} or \cite{Bakalov2000}.
For a more pedestrian treatment, see \cite{Freedman2002simulation} or \cite{Beverland2004.}

@@

{\bf Axiom III.}
%Gluing.
Denote a surface $M$ with (at least) two boundary
components labelled $a, b$ as $M_{a,b}$. 
Let $N$ be the surface obtained from $M$ by gluing
these two boundary components together.
If we constrain $b=\hat{a}$ then the fusion space
of $M_{a,\hat{a}}$ embedds unitarily in the fusion
space of $N.$ Moreover, there is a unitary map
$$
    \bigoplus_{a\in\mathbb{A}} \F(M_{a,\hat{a}}) \xrightarrow{\cong} \F(N).
$$
A common operation is to glue two separate surfaces.
We can do this by first taking disjoint union (tensoring
the fusion spaces)
and then gluing.

Here we show this process applied to the disjoint union
%of two surfaces $M_a$ and $N_{\hat{a}}$. 
of two surfaces $M$ and $N$. 
We display the surface $N$ with the $\hat{a}$
boundary on the outside, to show more clearly how $N$ fits into $M$.
In the glued manifold we
indicate the placement of $M$ and $N$ and the seam
along which glueing occured.
\begin{center}
\includegraphics[]{pic-glue.pdf}
\end{center}

\emph{XXX show marked point on boundaries ?}

\emph{XXX show orientation of boundaries ?}
